The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-12-17 paper/mri_paper.tex
and more

@@

From the behavior of the second order velocity perturbations (Figure \ref{u_secondorder_by_Pm}) in the bulk of the flow (i.e. apart from the boundary layers), we gather that the MRI is saturating via a background shear reduction.

>>>>

We plot the total stress, or the sum of the Reynolds and Maxwell stresses,

\beq
\mathbb{T}(x, z) = u_x u_y - \frac{2}{\beta} B_x B_y.
\eeq

See Figure \ref{stress_uy_cuts}.

@@

From the behavior of the second order velocity perturbations (Figure \ref{u_secondorder_by_Pm}) in the bulk of the flow (i.e. apart from the boundary layers), we gather that the MRI is saturating via a background shear reduction. Recall that the linear shear profile means that the background shear is positive for negative values of $x$ and negative for positive values of $x$. Thus Figure \ref{u_secondorder_by_Pm} shows the azimuthal velocity perturbations resisting the background shear in the bulk of the flow
